\sc Estimating Evolutionary Parameters for Low Complexity Regions using an Approximate Bayesian Computation

### 2023-01-12 thesis_template/paper0904.tex
Jan 12 small update

\subsection{How will we use an ABC-MCMC}
Using the algorithm mentioned above for an ABC-MCMC, this study aims to better understand the evolutionary back-
ground/formation of protein LCRs. An ABC-MCMC will enable the prediction of two important evolutionary parameters,
mutation rate and indel rate. There is possibilty for the estimation of other parameters which will be explored upon investi-
gating the first two. We will utilize amino acid sequences in this study, one being the SRP40 protein found in Saccharomyces
cerevisiae, which is extremely biased in composition. This protein sequence will act as our observed data and we will compare
this observed data to our simulated data.

>>>>

\subsection{How will we use an ABC-MCMC - Oct 28 First draft}
Using the algorithm mentioned above for an ABC-MCMC, this study aims to better understand the evolutionary back-
ground/formation of protein LCRs. An ABC-MCMC will enable the prediction of two important evolutionary parameters,
mutation rate and indel rate. There is possibilty for the estimation of other parameters which will be explored upon investi-
gating the first two. We will utilize amino acid sequences in this study, one being the SRP40 protein found in Saccharomyces
cerevisiae, which is extremely biased in composition. This protein sequence will act as our observed data and we will compare
this observed data to our simulated data.
